---
title: "Interaction among nitrogen addition, litter quality and mesh size modulate litter decomposition in tropical forest"
author: "Yanlin Zhu, Denis Mburu Njoroge, Gbadamassi G.O. Dossa, Juan Zuo, Mareike Roeder, Douglas Schaefer, Yali Song"
date: (Created on 2025 September 23 and last updated on `r format(Sys.time(), "%a %b %d %Y %H:%M:%S")`)
output: 
#rmdformats::material
  html_document:
    fig_caption: yes #Enabling figure caption
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE # Enabling table of content (toc) on the left side of output
    toc_depth: 3 # Showing toc up to 3 headings below (i.e.,1, 1.1, 1.1.1)
    number_sections: TRUE # Number sections
    toc_float:
      collapsed: TRUE # Allows the toc to collapse if the reading section is not concerned
      smooth_scroll: TRUE # Allows smoth scrolling of toc
      toc: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, results="hide")
#Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```



# Introduction 
Nitrogen (N) deposition continues to impact terrestrial ecosystems and therein ecological functions. But how does N deposition interactively modify the effects of primary drivers of litter decomposition which are climate, litter quality, and soil fauna and microorganisms as well as their interactive effects on mixed litter decomposition remains unknown. We carried out a field decomposition experiment over a year in a tropical forest, SW China, mimicking N deposition by adding adhesive liquid N at three levels (0, 2, 6 g per litterbag) to mixed tree litters (each litterbag containing each two species) varying in quality (high, medium, low). Three mesh size (0.07, 2, 5 mm) were used for the litterbags aiming to control access by different groups of soil fauna to the litter. We also monitored the dynamics of some elements including carbon, nitrogen, calcium, phosphorus, potassium, magnesium, manganese, condensed tannins.  



# Data analysis

The average value of the initial chemical properties of the litter was calculated and one-way analysis of variance was conducted

First, we need to input the file "A2CC.csv" containing the following columns:

1. code is the species code in experiment 2 (A2) with H for High quality and M for Medium quality and L for Low quality high(low) N addition;

2. Totall_quality represents tree quality + N addition quality in this case it is the initial so no nitrogen added;

3. species	represents litter species in the mixture;

4. tree_quality	represents tree quality;

5. Nitrogen_added	represents Nitrogen added which is either 20 g or 5 g but because this file is for initial then nothing was added;

6. Number	represents the repeated measurement of the sample 1 for first measurement and 2 for the second measurement;

7. C_initial	represents initial carbon content;

8. N_initial	represents initial nitrogen content;

9. Ca_initial  	represents initial calcium content;

10. K_initial	represents initial potassium content;

11. Mg_initial	represents initial magnesium content;

12. Mn_initial	represents initial manganese content;

13. P_initial	represents initial phosphorus content;

14. Tannin_initial	represents initial condensed tannins content;

15. C/N	represents initial carbon-nitrogen ratio content;



```{r}
d1<- read.csv("A2CC.csv", header = TRUE, sep = ",", quote = "\"",
              dec = ".", fill = TRUE, comment.char = "",fileEncoding = 'latin1')

summary(d1)
d1$species=as.factor(d1$species)
d1$Totall_quality=as.factor(d1$Totall_quality)
d1$tree_quality=as.factor(d1$tree_quality)
d1$Nitrogen_added=as.factor(d1$Nitrogen_added)
d1$tree_quality=ordered(d1$tree_quality,levels=c("High","Medium","Low"))
#View(d1)
```


## Analysis of variance

```{r}
result <- aov(d1$initial_C ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_N ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_P ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_K ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_Ca ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)


result <- aov(d1$initial_Mg ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_Mn ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

result <- aov(d1$initial_Tannin ~ d1$tree_quality, data = d1)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```

## Table1

We compute the mean and standard error of the initial values of chemical elements.

```{r}
library(dplyr)
d1l<- d1%>% group_by(species,tree_quality,Nitrogen_added)%>%
  summarise(C=mean(initial_C),seC=sd(initial_C,na.rm = TRUE)/sqrt(n()),
            N=mean(initial_N),seN=sd(initial_N,na.rm = TRUE)/sqrt(n()),
            Ca=mean(initial_Ca),seCa=sd(initial_Ca,na.rm = TRUE)/sqrt(n()),
            K=mean(initial_K),seK=sd(initial_K,na.rm = TRUE)/sqrt(n()),
            Mg=mean(initial_Mg),seMg=sd(initial_Mg,na.rm = TRUE)/sqrt(n()),
            Mn=mean(initial_Mn),seMn=sd(initial_Mn,na.rm = TRUE)/sqrt(n()),
            P=mean(initial_P),seP=sd(initial_P,na.rm = TRUE)/sqrt(n()),
            Tannin=mean(initial_Tannin),seTannin=sd(initial_Tannin,na.rm = TRUE)/sqrt(n()),
            "C/N"=mean(C/N),"seCN"=sd(C/N,na.rm = TRUE)/sqrt(n()),)

#View(d1l)
```

Soil fauna are major drivers of decomposition in terrestrial ecosystems, nitrogen deposition changes the total available soil N, which affects decomposers' growth and activities, and hence litter decomposition and nutrient release. However, how interactions between N addition and soil fauna affect decomposition and nutrient release vary with litter quality remains unknown. Therefore, we used different litterbag mesh size for the decomposition experiment (0.07, 2, 5 mm). 


## First import the experiment data file

We import the file named "A2_February 2026.csv" which contains the mass loss information.
The file A2 represents the main experimental file for this project. Below we describe each column content: 

1. Experiment_type: Experiment2 consisting of a tree mixture (A2) with two N addition levels, 5 g and 20 g per each litterbag; 

2. code: A2FT(H) represents mixture of high quality litter, A2FT(M) mixture of Medium quality litter, A2FT(L) respresents mixture of low quality litter, A2HH represents with mixture of High quality litter+ high N level added (20 g), A2HL represents with mixture of High quality litter + low N level added (5 g), A2MH represents with mixture of Medium quality litter + high N level added (20 g), A2ML represents with mixture of Medium quality litter + low N level added (5 g), A2LH represents with mixture of Low quality litter + high N level added (20 g), A2LL represents with mixture of Low quality litter + low N level added (5 g);

3. tree_quality: tree litter quality ( with H for High quality and M for Medium quality and L for Low quality high(low);

4. species: tree species;

5. quality: tree quality + N addition quality;

6. Nitrogen_added: Nitrogen addition (N 20 for 20 gram of N addition on the litter in each litterbag or N 5 for 5 gram of N addition on the litter in each litterbag);

7. mix_type: mixture type (tree mixture);

8. species_richness: species richness;

9. number: Prior to placement in the sample plots, each treatment consisted of 15 samples (12 for field decomposition across four decomposition periods with three replicates each, and 3 for determining transportation loss);

10. litter_type_quality_tree_1: tree species 1 (mass);

11. litter_type_quality_tree_2: tree species 2 (mass);

12. quality_N: N (mass);

13. mesh_size: litter bag mesh size (To control the entry litter bags of soil fauna of different sizes);

14. total_mass_g: total mass inside the litter bag (litter + N);

15. sample_plot: 12 subplots;

16. plot: 3 plots;

17. harvest: harvest sequence;

18. handling_loss_bags: change of litter mass during transport of litterbags from lab to incubation field (detect the loss on the way);

19. handling_loss: change in litter mass during transportation;

20. initial_mass_g: The initial mass in the litter bag after removing the losses during transportation;

21. Time_at_harvest: harvesting time (number of days);

22. final_mass_g: The mass of litter obtained at different harvest times.


```{r}
A2<- read.csv("A2.csv", header = TRUE, sep = ",", quote = "\"",
              dec = ".", fill = TRUE, comment.char = "",fileEncoding = 'latin1')
A2<-subset(A2, !is.na(final_mass_g))
head(A2)

#Convert to factor before ordering from high to low
str(A2$tree_quality)
A2$tree_quality
levels(A2$tree_quality)
A2$tree_quality <- as.factor(A2$tree_quality)
levels(A2$tree_quality)

A2$tree_quality <- ordered(A2$tree_quality, levels = c("Low","Medium","High" ))
levels(A2$tree_quality)

#Convert to factor before ordering from high N addition to low concentration (0 gram), please note that "zero"
## means no addition for single species
A2$Nitrogen_added <- as.factor(A2$Nitrogen_added)
levels(A2$Nitrogen_added)
#View(A2)
A2$Nitrogen_added <- ordered(A2$Nitrogen_added, levels = c("N_0", "N_2", "N_6"))
levels(A2$Nitrogen_added)

#Convert Time_at_harvest to factor before ordering
A2$Time_at_harvest
levels(A2$Time_at_harvest)
A2$Time_at_harvest<-as.factor(A2$Time_at_harvest)
levels(A2$Time_at_harvest)

A2$Time_at_harvest<-ordered(A2$Time_at_harvest, levels=c("30","60","220","365"))
levels(A2$Time_at_harvest)

str(A2)

#Convert mesh_size to factor
levels(A2$mesh_size)
A2$mesh_size<-as.factor(A2$mesh_size)

# Check our data frame quality
str(A2)

```


## Calculation“loss_rate”
Prior to any analysis, we need to calculate decomposition rate or mass loss. Here we call it loss_rate. When handling loss is negative, this means there is actual loss during handling from lab to field. Thus the initial mass is the measured mass in lab corrected from the handling loss. 

For two species in mixture there is N addition at different levels, the handling loss consists of both loss of litter after the N was added, we need to be careful of how to compute this. We need some assumption, the handling loss consists of both added N and the litter. Therefore, handling_loss= measured handling_loss*(mass of litter before adding N/total_mass_g after adding N). Only after we measured this, we could then proceed to compute the mixture mass loss. 



## two species

```{r}
dat=A2[A2$species_richness=="2",]
dat$mass=dat$litter_type_quality_tree_1+dat$litter_type_quality_tree_2
dat_1=dat[dat$Nitrogen_added=="N_0",]
dat_11=dat_1[dat_1$handlin_loss<=0,]
dat_11$loss_rate=(dat_11$mass-dat_11$final_mass_g+dat_11$handlin_loss)/(dat_11$mass+dat_11$handlin_loss)
dat_21=dat_1[dat_1$handlin_loss>0,]
dat_21$loss_rate=(dat_21$mass-dat_21$final_mass_g)/(dat_21$mass)
dat_1=rbind(dat_11,dat_21)

dat_2=dat[dat$Nitrogen_added!="N_0",]
#View(dat_2)
dat_2$handlin_loss=dat_2$handlin_loss*(dat_2$mass/dat_2$total_mass_g)
dat_2$loss_rate=(dat_2$mass-dat_2$final_mass_g+dat_2$handlin_loss)/(dat_2$mass+dat_2$handlin_loss)
dat =rbind(dat_1,dat_2)
#View(dat)
dat_c=dat

#Calculate loss rate the litter of different tree quality and  different times
library(dplyr)
dat_ml1<- dat%>% group_by(tree_quality,Time_at_harvest)%>%
  dplyr::summarise(ml= mean(loss_rate),
                   sd= sd(loss_rate),
                   se=sd(loss_rate,na.rm = TRUE)/sqrt(n()))
#View(dat_ml1)
```

### Mass loss at 30 days after incubation

```{r, results="hide"}
#draw plot
library(dplyr)
library(ggplot2)
dat$Nitrogen_added <- factor(dat$Nitrogen_added, levels = c("N_0", "N_2", "N_6"),
                             labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
dat1 <- dat[dat$Time_at_harvest=="30",]
dat_ml1<- dat1%>% group_by(tree_quality,Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_rate),
                   sd= sd(loss_rate),
                   se=sd(loss_rate,na.rm = TRUE)/sqrt(n()))
dat_ml1$tree_quality<-ordered(dat_ml1$tree_quality, levels=c("High","Medium","Low"))
levels(dat_ml1$tree_quality)


pt1 <-ggplot(dat_ml1,aes(tree_quality,ml,shape=Nitrogen_added,color=mesh_size))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,1))+
  scale_colour_manual(values=c("#5867AF","#4C9AC9","#E2745E"))+
  scale_shape_discrete(
    name = "N addition",
    labels = function(x) parse(text = x))+
  labs( colour="mesh_size",title="(a)30days")+
  xlab("Litter quality")+
  ylab("Mass loss proportion")+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(14)))+
  theme(legend.position = "none", 
        legend.direction = "vertical",
        legend.text = element_text(size=14))+
  theme(legend.title=element_text(size=(14)))+
  theme(axis.title = element_text(family = "palatino", size = (14), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (13)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

pt1

```
### Mass loss at 60 days after incubation

```{r, results="hide"}
dat2 <-dat[dat$Time_at_harvest=="60",]
dat_ml2<- dat2%>% group_by(tree_quality,Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_rate),
                   sd= sd(loss_rate),
                   se=sd(loss_rate,na.rm = TRUE)/sqrt(n()))
dat_ml2$tree_quality<-ordered(dat_ml2$tree_quality, levels=c("High","Medium","Low"))
levels(dat_ml2$tree_quality)

pt2<-ggplot(dat_ml2,aes(tree_quality,ml,shape=Nitrogen_added,color=mesh_size))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml2$ml+dat_ml2$se,ymin=dat_ml2$ml-dat_ml2$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,1))+
  scale_colour_manual(values=c("#5867AF","#4C9AC9","#E2745E"))+
  scale_shape_discrete(
    name = "N addition",
    labels = function(x) parse(text = x))+
  labs(colour="mesh_size",title="(b)60days")+ xlab("Litter quality")+
  ylab("Mass loss proportion")+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(14)))+
  theme(legend.position = "none", 
        legend.direction = "vertical",
        legend.text = element_text(size=14))+
  theme(legend.title=element_text(size=(14)))+
  theme(axis.title = element_text(family = "palatino", size = (14), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (13)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

pt2

```

### Mass loss at 220 days after incubation

```{r, results="hide"}
dat3<-dat[dat$Time_at_harvest=="220",]
dat_ml3<- dat3%>% group_by(tree_quality,Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_rate),
                   sd= sd(loss_rate),
                   se=sd(loss_rate,na.rm = TRUE)/sqrt(n()))
dat_ml3$tree_quality<-ordered(dat_ml3$tree_quality, levels=c("High","Medium","Low"))
levels(dat_ml3$tree_quality)

pt3<-ggplot(dat_ml3,aes(tree_quality,ml,shape=Nitrogen_added,color=mesh_size))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml3$ml+dat_ml3$se,ymin=dat_ml3$ml-dat_ml3$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,1))+
  scale_colour_manual(values=c("#5867AF","#4C9AC9","#E2745E"))+ 
  scale_shape_discrete(
    name = "N addition",
    labels = function(x) parse(text = x))+
  labs(colour="mesh_size",title="(c)220days")+ xlab("Litter quality")+
  ylab("Mass loss proportion")+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(14)))+
  theme(legend.position = "none", 
        legend.direction = "vertical",
        legend.text = element_text(size=14))+
  theme(legend.title=element_text(size=(14)))+
  theme(axis.title = element_text(family = "palatino", size = (14), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (13)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

pt3

```



### Mass loss at 365 days after incubation

```{r, results="hide"}
dat4<-dat[dat$Time_at_harvest=="365",]
dat_ml4<- dat4%>% group_by(tree_quality,Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_rate),
                   sd= sd(loss_rate),
                   se=sd(loss_rate,na.rm = TRUE)/sqrt(n()))
dat_ml4$tree_quality<-ordered(dat_ml4$tree_quality, levels=c("High","Medium","Low"))
levels(dat_ml4$tree_quality)
pt4 <-ggplot(dat_ml4,aes(tree_quality,ml,shape=Nitrogen_added,color=mesh_size))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",width=0.3,size=3)+
  geom_errorbar(ymax=dat_ml4$ml+dat_ml4$se,ymin=dat_ml4$ml-dat_ml4$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,1))+
  scale_colour_manual(values=c("#5867AF","#4C9AC9","#E2745E"))+
  scale_shape_discrete(
    name = "N addition",
    labels = function(x) parse(text = x))+
  labs( shape="N addition",colour="mesh_size",title="(d)365days")+ xlab("Litter quality")+
  ylab("Mass loss proportion")+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(14)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=14))+
  theme(legend.title=element_text(size=(14)))+
  theme(axis.title = element_text(family = "palatino", size = (14), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (13)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

pt4
```


### Mass loss combination of all four harvests

Mass loss across tree litter qualities in the presence of different decomposer groups across harvest (365 days of field exposure of the litterbags).


```{r}

library(patchwork)

# Put panels together
Graphs_plot <-pt1+pt2+pt3+pt4
Graphs_plot
ggsave(
  filename = paste0("figure S1.png"),
  plot =Graphs_plot,
  width = 13,
  height =9,
  dpi = 300,
  bg = "white"
)
```

Figure S1


## Decay rates

We have many variables that could potentially interact with time and may cause difficulty to understand the general trend, thus before modeling, we computed the decay rates using "neg.exp" regression within the litter fitter package, doing so could eliminate the many levels for the time variable.

```{r}
library(litterfitter)
dat=dat_c
#View(dat)
dat$Nitrogen_added <- factor(dat$Nitrogen_added, levels = c("N_0", "N_2", "N_6"),
                             labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
dat$Time_at_harvest=as.numeric(as.character(dat$Time_at_harvest))
dat$loss_rate_adj <- dat$loss_rate
dat <- subset(dat, loss_rate_adj >= 0)
dat$loss_rate_adj[dat$loss_rate_adj == 1] <- 0.999
dat$loss_rate_adj[dat$loss_rate_adj == 0] <- 0.001
dat$mass.remaining=(1-dat$loss_rate_adj)
dat$t=dat$Time_at_harvest/365

dat <- subset(dat, mass.remaining != 0)
#View(dat)

##Separate data presentation :tree_quality="high"，"med"，"low"，Nitrogen_added ="N0g"，"N2g"，"N5g"，mesh_size="5mm"，"2mm"，"0.07mm",plot="plot1","plot2","plot3"

###tree_quality="high"，"med"，"low"，Nitrogen_added ="N0g"
thigh=dat[dat$tree_quality=="High",]
tmed=dat[dat$tree_quality=="Medium",]
tlow=dat[dat$tree_quality=="Low",]
thigh_0=thigh[thigh$Nitrogen_added =="N[0]",]
#View(thigh)

##tree_quality="high",Nitrogen_added ="N0g",mesh_size =="5mm",(plot="plot1","plot2","plot3")
thigh_0_5=thigh_0[thigh_0$mesh_size =="5 mm",]
#View(thigh_0_5)
thigh_0_5_plot1=thigh_0_5[thigh_0_5$plot=="plot1",]
result<- fit_litter(
  thigh_0_5_plot1$t,
  thigh_0_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)

thigh_0_5_plot1$k=result$optimFit$par


thigh_0_5_plot2=thigh_0_5[thigh_0_5$plot=="plot2",]
result <- fit_litter(
  thigh_0_5_plot2$t,
  thigh_0_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_5_plot2$k=result$optimFit$par


thigh_0_5_plot3=thigh_0_5[thigh_0_5$plot=="plot3",]
result <- fit_litter(
  thigh_0_5_plot3$t,
  thigh_0_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_5_plot3$k=result$optimFit$par


##tree_quality="Thigh",Nitrogen_added ="N0g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
thigh_0_2=thigh_0[thigh_0$mesh_size =="2 mm",]
thigh_0_2_plot1=thigh_0_2[thigh_0_2$plot=="plot1",]
result <- fit_litter(
  thigh_0_2_plot1$t,
  thigh_0_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_2_plot1$k=result$optimFit$par


thigh_0_2_plot2=thigh_0_2[thigh_0_2$plot=="plot2",]
result <- fit_litter(
  thigh_0_2_plot2$t,
  thigh_0_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_2_plot2$k=result$optimFit$par


thigh_0_2_plot3=thigh_0_2[thigh_0_2$plot=="plot3",]
result <- fit_litter(
  thigh_0_2_plot3$t,
  thigh_0_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_2_plot3$k=result$optimFit$par

##tree_quality="Thigh",Nitrogen_added ="N0g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
thigh_0_0.07=thigh_0[thigh_0$mesh_size =="0.07 mm",]
thigh_0_0.07_plot1=thigh_0_0.07[thigh_0_0.07$plot=="plot1",]
result <- fit_litter(
  thigh_0_0.07_plot1$t,
  thigh_0_0.07_plot1$mass.remaining,
  model = "neg.exp",  
  lower = 1e-6,
  iters = 1000
)

print(result)
thigh_0_0.07_plot1$k=result$optimFit$par


thigh_0_0.07_plot2=thigh_0_0.07[thigh_0_0.07$plot=="plot2",]
result <- fit_litter(
  thigh_0_0.07_plot2$t,
  thigh_0_0.07_plot2$mass.remaining,
  model = "neg.exp",  
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_0.07_plot2$k=result$optimFit$par


thigh_0_0.07_plot3=thigh_0_0.07[thigh_0_0.07$plot=="plot3",]
result <- fit_litter(
  thigh_0_0.07_plot3$t,
  thigh_0_0.07_plot3$mass.remaining,
  model = "neg.exp",  
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_0_0.07_plot3$k=result$optimFit$par



##tree_quality="Thigh",Nitrogen_added ="N2g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
thigh_2=thigh[thigh$Nitrogen_added =="N[2]",]
#View(thigh)
thigh_2_5=thigh_2[thigh_2$mesh_size =="5 mm",]
thigh_2_5_plot1=thigh_2_5[thigh_2_5$plot=="plot1",]
result <- fit_litter(
  thigh_2_5_plot1$t,
  thigh_2_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_5_plot1$k=result$optimFit$par

thigh_2_5_plot2=thigh_2_5[thigh_2_5$plot=="plot2",]
result <- fit_litter(
  thigh_2_5_plot2$t,
  thigh_2_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_5_plot2$k=result$optimFit$par


thigh_2_5_plot3=thigh_2_5[thigh_2_5$plot=="plot3",]
result <- fit_litter(
  thigh_2_5_plot3$t,
  thigh_2_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_5_plot3$k=result$optimFit$par


##tree_quality="Thigh",Nitrogen_added ="N2g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
thigh_2_2=thigh_2[thigh_2$mesh_size =="2 mm",]
thigh_2_2_plot1=thigh_2_2[thigh_2_2$plot=="plot1",]
result <- fit_litter(
  thigh_2_2_plot1$t,
  thigh_2_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_2_plot1$k=result$optimFit$par

thigh_2_2_plot2=thigh_2_2[thigh_2_2$plot=="plot2",]
result <- fit_litter(
  thigh_2_2_plot2$t,
  thigh_2_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_2_plot2$k=result$optimFit$par


thigh_2_2_plot3=thigh_2_2[thigh_2_2$plot=="plot3",]
result <- fit_litter(
  thigh_2_2_plot3$t,
  thigh_2_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_2_plot3$k=result$optimFit$par


##tree_quality="Thigh",Nitrogen_added ="N2g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
thigh_2_0.07=thigh_2[thigh_2$mesh_size =="0.07 mm",]
thigh_2_0.07_plot1=thigh_2_0.07[thigh_2_0.07$plot=="plot1",]
result <- fit_litter(
  thigh_2_0.07_plot1$t,
  thigh_2_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_0.07_plot1$k=result$optimFit$par

thigh_2_0.07_plot2=thigh_2_0.07[thigh_2_0.07$plot=="plot2",]
result <- fit_litter(
  thigh_2_0.07_plot2$t,
  thigh_2_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_0.07_plot2$k=result$optimFit$par


thigh_2_0.07_plot3=thigh_2_0.07[thigh_2_0.07$plot=="plot3",]
result <- fit_litter(
  thigh_2_0.07_plot3$t,
  thigh_2_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_2_0.07_plot3$k=result$optimFit$par




##tree_quality="Thigh",Nitrogen_added ="N6g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
thigh_6=thigh[thigh$Nitrogen_added =="N[6]",]
thigh_6_5=thigh_6[thigh_6$mesh_size =="5 mm",]
thigh_6_5_plot1=thigh_6_5[thigh_6_5$plot=="plot1",]
result <- fit_litter(
  thigh_6_5_plot1$t,
  thigh_6_5_plot1$mass.remaining,
  model = "neg.exp",
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_5_plot1$k=result$optimFit$par


thigh_6_5_plot2=thigh_6_5[thigh_6_5$plot=="plot2",]
result <- fit_litter(
  thigh_6_5_plot2$t,
  thigh_6_5_plot2$mass.remaining,
  model = "neg.exp",
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_5_plot2$k=result$optimFit$par



thigh_6_5_plot3=thigh_6_5[thigh_6_5$plot=="plot3",]
result <- fit_litter(
  thigh_6_5_plot3$t,
  thigh_6_5_plot3$mass.remaining,
  model = "neg.exp",
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_5_plot3$k=result$optimFit$par





##tree_quality="Thigh",Nitrogen_added ="N6g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
thigh_6_2=thigh_6[thigh_6$mesh_size =="2 mm",]
thigh_6_2_plot1=thigh_6_2[thigh_6_2$plot=="plot1",]
result <- fit_litter(
  thigh_6_2_plot1$t,
  thigh_6_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_2_plot1$k=result$optimFit$par

thigh_6_2_plot2=thigh_6_2[thigh_6_2$plot=="plot2",]
result <- fit_litter(
  thigh_6_2_plot2$t,
  thigh_6_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_2_plot2$k=result$optimFit$par


thigh_6_2_plot3=thigh_6_2[thigh_6_2$plot=="plot3",]
result <- fit_litter(
  thigh_6_2_plot3$t,
  thigh_6_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_2_plot3$k=result$optimFit$par


##tree_quality="Thigh",Nitrogen_added ="N6g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
thigh_6_0.07=thigh_6[thigh_6$mesh_size =="0.07 mm",]
thigh_6_0.07_plot1=thigh_6_0.07[thigh_6_0.07$plot=="plot3",]
result <- fit_litter(
  thigh_6_0.07_plot1$t,
  thigh_6_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_0.07_plot1$k=result$optimFit$par

thigh_6_0.07_plot2=thigh_6_0.07[thigh_6_0.07$plot=="plot2",]
result <- fit_litter(
  thigh_6_0.07_plot2$t,
  thigh_6_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_0.07_plot2$k=result$optimFit$par

thigh_6_0.07_plot3=thigh_6_0.07[thigh_6_0.07$plot=="plot3",]
result <- fit_litter(
  thigh_6_0.07_plot3$t,
  thigh_6_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
thigh_6_0.07_plot3$k=result$optimFit$par

##tree_quality="Tmed",Nitrogen_added ="N0g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tmed_0=tmed[tmed$Nitrogen_added =="N[0]",]
tmed_0_5=tmed_0[tmed_0$mesh_size =="5 mm",]
tmed_0_5_plot1=tmed_0_5[tmed_0_5$plot=="plot1",]
result <- fit_litter(
  tmed_0_5_plot1$t,
  tmed_0_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_5_plot1$k=result$optimFit$par

tmed_0_5_plot2=tmed_0_5[tmed_0_5$plot=="plot2",]
result <- fit_litter(
  tmed_0_5_plot2$t,
  tmed_0_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_5_plot2$k=result$optimFit$par

tmed_0_5_plot3=tmed_0_5[tmed_0_5$plot=="plot3",]
result <- fit_litter(
  tmed_0_5_plot3$t,
  tmed_0_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_5_plot3$k=result$optimFit$par

##tree_quality="Tmed",Nitrogen_added ="N0g",mesh_size ="2 mm",(plot="plot1","plot2","plot3")
tmed_0_2=tmed_0[tmed_0$mesh_size =="2 mm",]
tmed_0_2_plot1=tmed_0_2[tmed_0_2$plot=="plot1",]
result <- fit_litter(
  tmed_0_2_plot1$t,
  tmed_0_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_2_plot1$k=result$optimFit$par


tmed_0_2_plot2=tmed_0_2[tmed_0_2$plot=="plot2",]
result <- fit_litter(
  tmed_0_2_plot2$t,
  tmed_0_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_2_plot2$k=result$optimFit$par

tmed_0_2_plot3=tmed_0_2[tmed_0_2$plot=="plot3",]
result <- fit_litter(
  tmed_0_2_plot3$t,
  tmed_0_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_2_plot3$k=result$optimFit$par

##tree_quality="Tmed",Nitrogen_added ="N0g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tmed_0_0.07=tmed_0[tmed_0$mesh_size =="0.07 mm",]
tmed_0_0.07_plot1=tmed_0_0.07[tmed_0_0.07$plot=="plot1",]
result <- fit_litter(
  tmed_0_0.07_plot1$t,
  tmed_0_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_0.07_plot1$k=result$optimFit$par

tmed_0_0.07_plot2=tmed_0_0.07[tmed_0_0.07$plot=="plot2",]
result <- fit_litter(
  tmed_0_0.07_plot2$t,
  tmed_0_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_0.07_plot2$k=result$optimFit$par

tmed_0_0.07_plot3=tmed_0_0.07[tmed_0_0.07$plot=="plot3",]
result <- fit_litter(
  tmed_0_0.07_plot3$t,
  tmed_0_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_0_0.07_plot3$k=result$optimFit$par


##tree_quality="Tmed",Nitrogen_added ="N2g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tmed_2=tmed[tmed$Nitrogen_added =="N[2]",]
tmed_2_5=tmed_2[tmed_2$mesh_size =="5 mm",]
tmed_2_5_plot1=tmed_2_5[tmed_2_5$plot=="plot1",]
result <- fit_litter(
  tmed_2_5_plot1$t,
  tmed_2_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_5_plot1$k=result$optimFit$par


tmed_2_5_plot2=tmed_2_5[tmed_2_5$plot=="plot2",]
result <- fit_litter(
  tmed_2_5_plot2$t,
  tmed_2_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_5_plot2$k=result$optimFit$par


tmed_2_5_plot3=tmed_2_5[tmed_2_5$plot=="plot3",]
result <- fit_litter(
  tmed_2_5_plot3$t,
  tmed_2_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_5_plot3$k=result$optimFit$par


##tree_quality="Tmed",Nitrogen_added ="N2g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
tmed_2_2=tmed_2[tmed_2$mesh_size =="2 mm",]
tmed_2_2_plot1=tmed_2_2[tmed_2_2$plot=="plot1",]
result <- fit_litter(
  tmed_2_2_plot1$t,
  tmed_2_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_2_plot1$k=result$optimFit$par


tmed_2_2_plot2=tmed_2_2[tmed_2_2$plot=="plot2",]
result <- fit_litter(
  tmed_2_2_plot2$t,
  tmed_2_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_2_plot2$k=result$optimFit$par


tmed_2_2_plot3=tmed_2_2[tmed_2_2$plot=="plot3",]
result <- fit_litter(
  tmed_2_2_plot3$t,
  tmed_2_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_2_plot3$k=result$optimFit$par


##tree_quality="Tmed",Nitrogen_added ="N2g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tmed_2_0.07=tmed_2[tmed_2$mesh_size =="0.07 mm",]
tmed_2_0.07_plot1=tmed_2_0.07[tmed_2_0.07$plot=="plot1",]
result <- fit_litter(
  tmed_2_0.07_plot1$t,
  tmed_2_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_0.07_plot1$k=result$optimFit$par


tmed_2_0.07_plot2=tmed_2_0.07[tmed_2_0.07$plot=="plot2",]
result <- fit_litter(
  tmed_2_0.07_plot2$t,
  tmed_2_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_0.07_plot2$k=result$optimFit$par


tmed_2_0.07_plot3=tmed_2_0.07[tmed_2_0.07$plot=="plot3",]
result <- fit_litter(
  tmed_2_0.07_plot3$t,
  tmed_2_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_2_0.07_plot3$k=result$optimFit$par



##tree_quality="Tmed",Nitrogen_added ="N6g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tmed_6=tmed[tmed$Nitrogen_added =="N[6]",]
tmed_6_5=tmed_6[tmed_6$mesh_size =="5 mm",]
tmed_6_5_plot1=tmed_6_5[tmed_6_5$plot=="plot1",]
result <- fit_litter(
  tmed_6_5_plot1$t,
  tmed_6_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_5_plot1$k=result$optimFit$par


tmed_6_5_plot2=tmed_6_5[tmed_6_5$plot=="plot2",]
result <- fit_litter(
  tmed_6_5_plot2$t,
  tmed_6_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_5_plot2$k=result$optimFit$par

tmed_6_5_plot3=tmed_6_5[tmed_6_5$plot=="plot3",]
result <- fit_litter(
  tmed_6_5_plot3$t,
  tmed_6_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_5_plot3$k=result$optimFit$par

##tree_quality="Tmed",Nitrogen_added ="6g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
tmed_6_2=tmed_6[tmed_6$mesh_size =="2 mm",]
tmed_6_2_plot1=tmed_6_2[tmed_6_2$plot=="plot1",]
result <- fit_litter(
  tmed_6_2_plot1$t,
  tmed_6_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_2_plot1$k=result$optimFit$par

tmed_6_2_plot2=tmed_6_2[tmed_6_2$plot=="plot2",]
result <- fit_litter(
  tmed_6_2_plot2$t,
  tmed_6_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_2_plot2$k=result$optimFit$par


tmed_6_2_plot3=tmed_6_2[tmed_6_2$plot=="plot3",]
result <- fit_litter(
  tmed_6_2_plot3$t,
  tmed_6_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_2_plot3$k=result$optimFit$par


##tree_quality="Tmed",Nitrogen_added ="N6g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tmed_6_0.07=tmed_6[tmed_6$mesh_size =="0.07 mm",]
tmed_6_0.07_plot1=tmed_6_0.07[tmed_6_0.07$plot=="plot1",]
result <- fit_litter(
  tmed_6_0.07_plot1$t,
  tmed_6_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_0.07_plot1$k=result$optimFit$par

tmed_6_0.07_plot2=tmed_6_0.07[tmed_6_0.07$plot=="plot2",]
result <- fit_litter(
  tmed_6_0.07_plot2$t,
  tmed_6_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_0.07_plot2$k=result$optimFit$par


tmed_6_0.07_plot3=tmed_6_0.07[tmed_6_0.07$plot=="plot3",]
result <- fit_litter(
  tmed_6_0.07_plot3$t,
  tmed_6_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tmed_6_0.07_plot3$k=result$optimFit$par


##tree_quality="Tlow",Nitrogen_added ="N0g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tlow_0=tlow[tlow$Nitrogen_added =="N[0]",]
tlow_0_5=tlow_0[tlow_0$mesh_size =="5 mm",]
tlow_0_5_plot1=tlow_0_5[tlow_0_5$plot=="plot1",]
result <- fit_litter(
  tlow_0_5_plot1$t,
  tlow_0_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_5_plot1$k=result$optimFit$par


tlow_0_5_plot2=tlow_0_5[tlow_0_5$plot=="plot2",]
result <- fit_litter(
  tlow_0_5_plot2$t,
  tlow_0_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_5_plot2$k=result$optimFit$par

tlow_0_5_plot3=tlow_0_5[tlow_0_5$plot=="plot3",]
result <- fit_litter(
  tlow_0_5_plot3$t,
  tlow_0_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_5_plot3$k=result$optimFit$par

##tree_quality="Tlow",Nitrogen_added ="N0g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
tlow_0_2=tlow_0[tlow_0$mesh_size =="2 mm",]
tlow_0_2_plot1=tlow_0_2[tlow_0_2$plot=="plot1",]
result <- fit_litter(
  tlow_0_2_plot1$t,
  tlow_0_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_2_plot1$k=result$optimFit$par


tlow_0_2_plot2=tlow_0_2[tlow_0_2$plot=="plot2",]
result <- fit_litter(
  tlow_0_2_plot2$t,
  tlow_0_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_2_plot2$k=result$optimFit$par


tlow_0_2_plot3=tlow_0_2[tlow_0_2$plot=="plot3",]
result <- fit_litter(
  tlow_0_2_plot3$t,
  tlow_0_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_2_plot3$k=result$optimFit$par

##tree_quality="Tlow",Nitrogen_added ="N0g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tlow_0_0.07=tlow_0[tlow_0$mesh_size =="0.07 mm",]
tlow_0_0.07_plot1=tlow_0_0.07[tlow_0_0.07$plot=="plot1",]
result <- fit_litter(
  tlow_0_0.07_plot1$t,
  tlow_0_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_0.07_plot1$k=result$optimFit$par

tlow_0_0.07_plot2=tlow_0_0.07[tlow_0_0.07$plot=="plot2",]
result <- fit_litter(
  tlow_0_0.07_plot2$t,
  tlow_0_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_0.07_plot2$k=result$optimFit$par


tlow_0_0.07_plot3=tlow_0_0.07[tlow_0_0.07$plot=="plot3",]
result <- fit_litter(
  tlow_0_0.07_plot3$t,
  tlow_0_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_0_0.07_plot3$k=result$optimFit$par

##tree_quality="Tlow",Nitrogen_added ="N2g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tlow_2=tlow[tlow$Nitrogen_added =="N[2]",]
tlow_2_5=tlow_2[tlow_2$mesh_size =="5 mm",]
tlow_2_5_plot1=tlow_2_5[tlow_2_5$plot=="plot1",]
result <- fit_litter(
  tlow_2_5_plot1$t,
  tlow_2_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_5_plot1$k=result$optimFit$par


tlow_2_5_plot2=tlow_2_5[tlow_2_5$plot=="plot2",]
result <- fit_litter(
  tlow_2_5_plot2$t,
  tlow_2_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_5_plot2$k=result$optimFit$par


tlow_2_5_plot3=tlow_2_5[tlow_2_5$plot=="plot3",]
result <- fit_litter(
  tlow_2_5_plot3$t,
  tlow_2_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_5_plot3$k=result$optimFit$par




##tree_quality="Tlow",Nitrogen_added ="N2g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
tlow_2_2=tlow_2[tlow_2$mesh_size =="2 mm",]
tlow_2_2_plot1=tlow_2_2[tlow_2_2$plot=="plot1",]
result <- fit_litter(
  tlow_2_2_plot1$t,
  tlow_2_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_2_plot1$k=result$optimFit$par


tlow_2_2_plot2=tlow_2_2[tlow_2_2$plot=="plot2",]
result <- fit_litter(
  tlow_2_2_plot2$t,
  tlow_2_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_2_plot2$k=result$optimFit$par


tlow_2_2_plot3=tlow_2_2[tlow_2_2$plot=="plot3",]
result <- fit_litter(
  tlow_2_2_plot3$t,
  tlow_2_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_2_plot3$k=result$optimFit$par



##tree_quality="Tlow",Nitrogen_added ="N2g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tlow_2_0.07=tlow_2[tlow_2$mesh_size =="0.07 mm",]
tlow_2_0.07_plot1=tlow_2_0.07[tlow_2_0.07$plot=="plot1",]
result <- fit_litter(
  tlow_2_0.07_plot1$t,
  tlow_2_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_0.07_plot1$k=result$optimFit$par


tlow_2_0.07_plot2=tlow_2_0.07[tlow_2_0.07$plot=="plot2",]
result <- fit_litter(
  tlow_2_0.07_plot2$t,
  tlow_2_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_0.07_plot2$k=result$optimFit$par


tlow_2_0.07_plot3=tlow_2_0.07[tlow_2_0.07$plot=="plot3",]
result <- fit_litter(
  tlow_2_0.07_plot3$t,
  tlow_2_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_2_0.07_plot3$k=result$optimFit$par


##tree_quality="Tlow",Nitrogen_added ="N6g",mesh_size ="5mm",(plot="plot1","plot2","plot3")
tlow_6=tlow[tlow$Nitrogen_added =="N[6]",]
tlow_6_5=tlow_6[tlow_6$mesh_size =="5 mm",]
tlow_6_5_plot1=tlow_6_5[tlow_6_5$plot=="plot1",]
result <- fit_litter(
  tlow_6_5_plot1$t,
  tlow_6_5_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-10,
  iters = 1000
)
print(result)
tlow_6_5_plot1$k=result$optimFit$par


tlow_6_5_plot2=tlow_6_5[tlow_6_5$plot=="plot2",]
result <- fit_litter(
  tlow_6_5_plot2$t,
  tlow_6_5_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-10,
  iters = 1000
)
print(result)
tlow_6_5_plot2$k=result$optimFit$par

tlow_6_5_plot3=tlow_6_5[tlow_6_5$plot=="plot3",]
result <- fit_litter(
  tlow_6_5_plot3$t,
  tlow_6_5_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-10,
  iters = 1000
)
print(result)
tlow_6_5_plot3$k=result$optimFit$par

##tree_quality="Tlow",Nitrogen_added ="N6g",mesh_size ="2mm",(plot="plot1","plot2","plot3")
tlow_6_2=tlow_6[tlow_6$mesh_size =="2 mm",]
tlow_6_2_plot1=tlow_6_2[tlow_6_2$plot=="plot1",]
result <- fit_litter(
  tlow_6_2_plot1$t,
  tlow_6_2_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_2_plot1$k=result$optimFit$par

tlow_6_2_plot2=tlow_6_2[tlow_6_2$plot=="plot2",]
result <- fit_litter(
  tlow_6_2_plot2$t,
  tlow_6_2_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_2_plot2$k=result$optimFit$par

tlow_6_2_plot3=tlow_6_2[tlow_6_2$plot=="plot3",]
result <- fit_litter(
  tlow_6_2_plot3$t,
  tlow_6_2_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_2_plot3$k=result$optimFit$par


##tree_quality="Tlow",Nitrogen_added ="N6g",mesh_size ="0.07mm",(plot="plot1","plot2","plot3")
tlow_6_0.07=tlow_6[tlow_6$mesh_size =="0.07 mm",]
tlow_6_0.07_plot1=tlow_6_0.07[tlow_6_0.07$plot=="plot1",]
result <- fit_litter(
  tlow_6_0.07_plot1$t,
  tlow_6_0.07_plot1$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_0.07_plot1$k=result$optimFit$par

tlow_6_0.07_plot2=tlow_6_0.07[tlow_6_0.07$plot=="plot2",]
result <- fit_litter(
  tlow_6_0.07_plot2$t,
  tlow_6_0.07_plot2$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_0.07_plot2$k=result$optimFit$par

tlow_6_0.07_plot3=tlow_6_0.07[tlow_6_0.07$plot=="plot3",]
result <- fit_litter(
  tlow_6_0.07_plot3$t,
  tlow_6_0.07_plot3$mass.remaining,
  model = "neg.exp", 
  lower = 1e-6,
  iters = 1000
)
print(result)
tlow_6_0.07_plot3$k=result$optimFit$par


##Combined result
dat1=rbind(thigh_0_5_plot1,thigh_0_5_plot2,thigh_0_5_plot3,thigh_0_2_plot1,thigh_0_2_plot2,thigh_0_2_plot3,
           thigh_0_0.07_plot1,thigh_0_0.07_plot2,thigh_0_0.07_plot3,thigh_2_5_plot1,thigh_2_5_plot2,thigh_2_5_plot3,
           thigh_2_2_plot1,thigh_2_2_plot2,thigh_2_2_plot3,thigh_2_0.07_plot1,thigh_2_0.07_plot2,thigh_2_0.07_plot3,
           thigh_6_5_plot1,thigh_6_5_plot2,thigh_6_5_plot3,thigh_6_2_plot1,thigh_6_2_plot2,thigh_6_2_plot3,
           thigh_6_0.07_plot1,thigh_6_0.07_plot2,thigh_6_0.07_plot3)

dat2=rbind(tmed_0_5_plot1,tmed_0_5_plot2,tmed_0_5_plot3,tmed_0_2_plot1,tmed_0_2_plot2,tmed_0_2_plot3,
           tmed_0_0.07_plot1,tmed_0_0.07_plot2,tmed_0_0.07_plot3,tmed_2_5_plot1,tmed_2_5_plot2,tmed_2_5_plot3,
           tmed_2_2_plot1,tmed_2_2_plot2,tmed_2_2_plot3,tmed_2_0.07_plot1,tmed_2_0.07_plot2,tmed_2_0.07_plot3,
           tmed_6_5_plot1,tmed_6_5_plot2,tmed_6_5_plot3,tmed_6_2_plot1,tmed_6_2_plot2,tmed_6_2_plot3,
           tmed_6_0.07_plot1,tmed_6_0.07_plot2,tmed_6_0.07_plot3)

dat3=rbind(tlow_0_5_plot1,tlow_0_5_plot2,tlow_0_5_plot3,tlow_0_2_plot1,tlow_0_2_plot2,tlow_0_2_plot3,
           tlow_0_0.07_plot1,tlow_0_0.07_plot2,tlow_0_0.07_plot3,tlow_2_5_plot1,tlow_2_5_plot2,tlow_2_5_plot3,
           tlow_2_2_plot1,tlow_2_2_plot2,tlow_2_2_plot3,tlow_2_0.07_plot1,tlow_2_0.07_plot2,tlow_2_0.07_plot3,
           tlow_6_5_plot1,tlow_6_5_plot2,tlow_6_5_plot3,tlow_6_2_plot1,tlow_6_2_plot2,tlow_6_2_plot3,
           tlow_6_0.07_plot1,tlow_6_0.07_plot2,tlow_6_0.07_plot3)

dat=rbind(dat1,dat2,dat3)
#View(dat)

```

### Draw plot figure 1

Next we need to draw the Figure 1 of the manuscript.


```{r}
dat_m<- dat%>% group_by(tree_quality,Nitrogen_added, mesh_size,plot,species)%>%
  dplyr::summarise(K= mean(k))
#View(dat_m)
nrow(dat_m)

#draw plot
library(dplyr)
library(ggplot2)
dat_ml1<- dat_m%>% group_by(tree_quality,Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(K),
                   sd= sd(K),
                   se=sd(K,na.rm = TRUE)/sqrt(n()))
dat_ml1$tree_quality<-ordered(dat_ml1$tree_quality, levels=c("High","Medium","Low"))
levels(dat_ml1$tree_quality)
#View(dat_ml1)

pt0 <-ggplot(dat_ml1,aes(tree_quality,ml,shape=Nitrogen_added,color=mesh_size))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=1.3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,5.5))+
  scale_colour_manual(values=c("#5867AF","#4C9AC9","#E2745E"))+
  scale_shape_discrete(
    name = "N addition",
    labels = function(x) parse(text = x))+
  labs( colour="Mesh size")+
  xlab("Litter quality")+
  ylab(expression(paste( "Decomposition constant k " ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (11)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

pt0


ggsave(
  filename = paste0("Figure 1.png"),
  plot =pt0,
  width = 6,
  height =4,
  dpi = 300,
  bg = "white"
)

```

Figure 1



## Establish the lmm model
We need to establish the linear mixed effect model (Table X).

```{r}
## Inverse normal transformation（Inverse Normal Transformation）
hist(dat_m$K)
dat_m$transrate <- log(dat_m$K)
hist(dat_m$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_m, transrate~Nitrogen_added*tree_quality*mesh_size+plot+(1|species))
summary(mod4)
anova(mod4)

mod3=lm(data=dat_m, transrate~Nitrogen_added*tree_quality*mesh_size+plot)
summary(mod3)
anova(mod4,mod3)

###似然比检验模型
#model_no_3way <- update(mod4, . ~ . - tree_quality:mesh_size:Nitrogen_added)

#anova(model_no_3way)
#anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")
```


This shows no difference between 0.07 mm and 2 mm mesh sizes litterbag decay rates, while 5 mm differs from 0.07 mm and 5 mm differs from 2 mm. 
```{r}
##one-way analysis of variance'mesh_size'
result <- aov(dat_m$transrate ~ dat_m$mesh_size, data = dat_m)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```




## Nutrient release (K, Ca, Mg, Mn, C, N, P, condensed tannins) from litter

A2c.csv is the file that contains the chemical element nutrient dynamics. It consists of the following columns:


1. Experiment_type	Experiment2;

2. code	A2FT(H) represents mixture of high quality litter, A2FT(M) mixture of Medium quality litter, A2FT(L) respresents mixture of low quality litter, A2HH represents with mixture of High quality litter+ high N level added (20 g), A2HL represents with mixture of High quality litter + low N level added (5 g), A2MH represents with mixture of Medium quality litter + high N level added (20 g), A2ML represents with mixture of Medium quality litter + low N level added (5 g), A2LH represents with mixture of Low quality litter + high N level added (20 g), A2LL represents with mixture of Low quality litter + low N level added (5 g);
	
3. tree_quality	tree quality;

4. species	tree species;

5. quality	tree quality + N addition quality;

6. Nitrogen_added	Nitrogen addition (N 20/N 5);

7. mix_type	mixture type (tree mixture);

8. species_richness	species richness; 

9. number	Repeated measurement of the sample;

10. mesh_size	litter bag mesh size(To control the entry litter bags of soil fauna of different sizes);

11. Time_at_harvest	harvesting time; 

12. final_mass_g	The mass of litter obtained at different harvest times; 

13. k	Decomposition rate constant k;

14. C_initial	represents initial carbon content; 

15. N_initial	represents initial nitrogen content;

16. Ca_initial represents initial calcium content;

17. K_initial	represents initial potassium content; 

18. Mg_initial	represents initial magnesium content; 

19. Mn_initial	represents initial manganese content; 

20. P_initial	represents initial phosphorus content;

21. Tannin_initial	represents initial condensed tannin content; 

22. C/N	represents initial carbon-nitrogen ratio content;

23. C	The carbon content at different decomposition times;

24. N	The nitrogen content at different decomposition times;

25. Ca	The calcium content at different decomposition times; 

26. K	The potassium content at different decomposition times;

27. Mg	The magnesium content at different decomposition times; 

28. Mn	The manganese content at different decomposition times; 

29. P	The phosphorus content at different decomposition times; 

30. Tannin	The condensed tannins content at different decomposition times;


```{r}
#setwd("C:/Users/86183/Desktop/A2shuju")
d1ll<- read.csv("A2c.csv", header = TRUE, sep = ",", quote = "\"",
                dec = ".", fill = TRUE, comment.char = "",fileEncoding = 'latin1')
summary(d1ll)

d1ll$C=as.numeric(d1ll$C)
d1ll$N=as.numeric(d1ll$N)
d1ll$P=as.numeric(d1ll$P)
d1ll$K=as.numeric(d1ll$K)
d1ll$Ca=as.numeric(d1ll$Ca)
d1ll$Mg=as.numeric(d1ll$Mg)
d1ll$Mn=as.numeric(d1ll$Mn)
d1ll$Tannin=as.numeric(d1ll$Tannin)

str(d1ll)

d1ll$initial_mass=d1ll$in_mass
d1ll$final_mass=d1ll$final_mass_g


#Calculate the nutrient release rate
d1ll$loss_K=((d1ll$K_initial*d1ll$initial_mass-d1ll$K*d1ll$final_mass)/(d1ll$K_initial*d1ll$initial_mass))*100
d1ll$loss_Ca=((d1ll$Ca_initial*d1ll$initial_mass-d1ll$Ca*d1ll$final_mass)/(d1ll$Ca_initial*d1ll$initial_mass))*100
d1ll$loss_Mg=((d1ll$Mg_initial*d1ll$initial_mass-d1ll$Mg*d1ll$final_mass)/(d1ll$Mg_initial*d1ll$initial_mass))*100
d1ll$loss_C=((d1ll$C_initial*d1ll$initial_mass-d1ll$C*d1ll$final_mass)/(d1ll$C_initial*d1ll$initial_mass))*100
d1ll$loss_N=((d1ll$N_initial*d1ll$initial_mass-d1ll$N*d1ll$final_mass)/(d1ll$N_initial*d1ll$initial_mass))*100
d1ll$loss_P=((d1ll$P_initial*d1ll$initial_mass-d1ll$P*d1ll$final_mass)/(d1ll$P_initial*d1ll$initial_mass))*100
d1ll$loss_Mn=((d1ll$Mn_initial*d1ll$initial_mass-d1ll$Mn*d1ll$final_mass)/(d1ll$Mn_initial*d1ll$initial_mass))*100
d1ll$loss_Tannin=((d1ll$Tannin_initial*d1ll$initial_mass-d1ll$Tannin*d1ll$final_mass)/(d1ll$Tannin_initial*d1ll$initial_mass))*100

#View(d1ll)


d1ll$Time_at_harvest=as.character(d1ll$Time_at_harvest)
d1ll$Time_at_harvest=as.numeric(d1ll$Time_at_harvest)
d1ll$mesh_size <- ordered(d1ll$mesh_size, levels = c("5 mm", "2 mm", "0.07 mm"))

#
d1ll_big=d1ll[d1ll$mesh_size=="5 mm",]
d1ll_med=d1ll[d1ll$mesh_size=="2 mm",]
d1ll_fine=d1ll[d1ll$mesh_size=="0.07 mm",]

#View(d1ll_big)
```


### Carbon dynamics 

```{r, results='hold'}
library(dplyr)
library(ggplot2)
#View(d1ll_big)
Carb_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                         aes(y =loss_C, x = Time_at_harvest, color =Nitrogen_added),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_C ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="N addition ", title = " 5 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Carbon release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=8,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
#Carb_5_mm
```



```{r}

result <- aov(d1ll_fine$loss_C ~ d1ll_fine$Nitrogen_added, data = d1ll_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_med$loss_C ~ d1ll_med$Nitrogen_added, data = d1ll_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_big$loss_C ~ d1ll_big$Nitrogen_added, data = d1ll_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```


```{r}

Carb_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                         aes(y =loss_C, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_C ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="N addition", title = " 2 mm", 
       x= "  Decomposition time (days)")+  ylab( expression(paste( " Carbon release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Carb_2_mm
```


```{r}
Carb_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                         aes(y =loss_C, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_C ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" N addition", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Carbon release rate (%)" )))+
  theme(legend.position = c(0.28,0.80))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
#Carb_0.07_mm


Carb=Carb_0.07_mm+Carb_2_mm+Carb_5_mm



#ggsave(filename="Figure S2carbon.png", plot=Carb, device="tiff",
#       height=3, width=9, units="in", dpi=600)

```


### Nitrogen dynamics

```{r}
library(dplyr)
library(ggplot2)

Nitr_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                         aes(y =loss_N, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_N ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" N addition ", title = " 5 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Nitrogen release rate (%)" )))+
  #theme(legend.position = c(0.2,0.85))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Nitr_5_mm
```


```{r}

Nitr_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                         aes(y =loss_N, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_N ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" N addition", title = "2 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Nitrogen release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Nitr_2_mm

```

```{r}
Nitr_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                         aes(y =loss_N, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_N ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" N addition", title = "0.07 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Nitrogen release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
#Nitr_0.07_mm

Nitr=Nitr_0.07_mm+Nitr_2_mm+Nitr_5_mm
#Nitr

ggsave(filename="Figure S2Nitrogen.png", plot=Nitr, device="tiff",
       height=3, width=9, units="in", dpi=600)

```


```{r}
result <- aov(d1ll_fine$loss_N ~ d1ll_fine$Nitrogen_added, data = d1ll_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_med$loss_N ~ d1ll_med$Nitrogen_added, data = d1ll_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_big$loss_N ~ d1ll_big$Nitrogen_added, data = d1ll_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```





### Phosphorus dynamics

```{r}
Phos_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                         aes(y =loss_P, x = Time_at_harvest, color = Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_P ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="N addition", title = "5 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Phosphorus release rate (%)" )))+
  #theme(legend.position = c(0.2,0.85))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Phos_5_mm
```

```{r}
Phos_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                         aes(y =loss_P, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_P ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="Litter type", title = "2 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Phosphorus release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Phos_2_mm
```

```{r}
Phos_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                         aes(y =loss_P, x = Time_at_harvest, color =Nitrogen_added ),
                         alpha = 0.4, 
                         size = 3,
                         width = 15,   # 水平抖动幅度
                         height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_P ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Phosphorus release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Phos_0.07_mm


Phos=Phos_0.07_mm+Phos_2_mm+Phos_5_mm
Phos
#ggsave(filename="Figure S2Phosphorus.png", plot=Phos, device="tiff",
#       height=3, width=9, units="in", dpi=600)
```

```{r}
result <- aov(d1ll_fine$loss_P~ d1ll_fine$Nitrogen_added, data = d1ll_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_med$loss_P ~ d1ll_med$Nitrogen_added, data = d1ll_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(d1ll_big$loss_P ~ d1ll_big$Nitrogen_added, data = d1ll_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```



### Potassium dynamics

```{r}
Pota_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                          aes(y =loss_K, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_K ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "5 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Potassium release rate (%)" )))+
  #theme(legend.position = c(0.2,0.85))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Pota_5_mm
```



```{r}
Pota_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                          aes(y =loss_K, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_K ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = " 2 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Potassium release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Pota_2_mm
```


```{r}

Pota_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                          aes(y =loss_K, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_K ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Potassium release rate (%)" )))+
  theme(legend.position = "none")+
  #theme(legend.position = c(0.28,0.80))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Pota_0.07_mm


Pota=Pota_0.07_mm+Pota_2_mm+Pota_5_mm
#Pota
#ggsave(filename="Figure S2Potassium.png", plot=Pota, device="tiff",
#       height=3, width=9, units="in", dpi=600)
```



### Calcium dynamics

```{r}
Calc_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                          aes(y =loss_Ca, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Ca ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "5 mm", 
       x= "Decomposition time ")+  ylab( expression(paste( "Calcium release rate (%)" )))+
  #theme(legend.position = c(0.2,0.85))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Calc_5_mm
```


```{r}
Calc_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                          aes(y =loss_Ca, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Ca ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "2 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( "Calcium release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Calc_2_mm

#View(d1ll_fine)
```

```{r}
Calc_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                          aes(y =loss_Ca, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Ca ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="N addition", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Calcium release rate (%)" )))+
  #theme(legend.position = "none")+
  theme(legend.position = c(0.2,0.8))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))
#Calc_0.07_mm

Calc=Calc_0.07_mm+Calc_2_mm+Calc_5_mm
Calc

#ggsave(filename="Figure S3Calcium.png", plot=Calc, device="tiff",
#       height=3, width=9, units="in", dpi=600)
```



### Magnesium dynamics

```{r}
Magn_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                          aes(y =loss_Mg, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mg ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "5 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Magnesium release rate (%)" )))+
  #theme(legend.position = c(0.2,0.85))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Magn_5_mm
```


```{r}
Magn_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                          aes(y =loss_Mg, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mg ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = " 2 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Magnesium release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Magn_2_mm
```


```{r}

Magn_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                          aes(y =loss_Mg, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mg ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-50,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Magnesium release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Magn_0.07_mm

Magn=Magn_0.07_mm+Magn_2_mm+Magn_5_mm
#Magn

#ggsave(filename="Figure S3Magnesium.png", plot=pK, device="tiff",
#       height=3, width=9, units="in", dpi=600)
```


### Manganese dynamics

```{r}
Mang_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                          aes(y =loss_Mn, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 5) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mn ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-100,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "5 mm", 
       x= "Decomposition time (days)")+  ylab( expression(paste( " Manganese release rate (%)" )))+
  theme(legend.position = "none")+
  #theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mang_5_mm
```

```{r}
Mang_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                          aes(y =loss_Mn, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 5) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mn ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-100,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "2 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Manganese release rate (%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mang_2_mm
```

```{r}

Mang_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                          aes(y =loss_Mn, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 5) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Mn,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(-100,100))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour ="Litter type", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( " Manganese release rate (%)" )))+
  theme(legend.position = "none")+
  #theme(legend.position = c(0.28,0.80))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mang_0.07_mm


Mang=Mang_0.07_mm+Mang_2_mm+Mang_5_mm
#Mang

#ggsave(filename="Figure S3Manganese.png", plot=Mang, device="tiff",
#       height=3, width=9, units="in", dpi=600)
```


### Condensed tannins dynamics


```{r}
Cond_5_mm=ggplot()+geom_jitter(data =d1ll_big,  
                          aes(y =loss_Tannin, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_big,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Tannin ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "5 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Tannins release rate(%)" )))+
  theme(legend.position = "none")+
  #theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Cond_5_mm
```


```{r}
Cond_2_mm=ggplot()+geom_jitter(data =d1ll_med,  
                          aes(y =loss_Tannin, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_med,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Tannin ,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "2 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Tannins release rate(%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Cond_2_mm
```


```{r}
Cond_0.07_mm=ggplot()+geom_jitter(data =d1ll_fine,  
                          aes(y =loss_Tannin, x = Time_at_harvest, color =Nitrogen_added ),
                          alpha = 0.4, 
                          size = 3,
                          width = 15,   # 水平抖动幅度
                          height = 0) +  
  geom_smooth(data=d1ll_fine,method = "lm",formula = y ~ poly(x, 2),se=FALSE,n=200, aes(x=Time_at_harvest , y=loss_Tannin,color=Nitrogen_added),size=1.0,linetype=1)+
  scale_y_continuous(limits = c(0,120))+
  scale_x_continuous(limits = c(0,400))+
  labs(colour =" Litter type", title = "0.07 mm", 
       x= " Decomposition time (days)")+  ylab( expression(paste( "Tannins release rate(%)" )))+
  theme(legend.position = "none")+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.8, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Cond_0.07_mm


Cond=Cond_0.07_mm+Cond_2_mm+Cond_5_mm
#Cond
#ggsave(filename="Figure S3Condensed tannins.png", plot=Cond, device="tiff",
#       height=3, width=9, units="in", dpi=600)




#View(d1ll)
```


For the supplementary figures S2 and S3, we need to create the patchwork.



```{r}
FigS2<-Carb/Nitr/Phos/Pota
ggsave(filename="Figure S2.png", plot=FigS2, device="tiff",
       height=3, width=9, units="in", dpi=600)
FigS2
```

Figure S2



```{r}
FigS3<-Calc/Magn/Mang/Cond
ggsave(filename="Figure S3.png", plot=FigS3, device="tiff",
       height=3, width=9, units="in", dpi=600)
FigS3

```

Figure S3




#calculation of k value of 
```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_C)
A1b$loss_C<- as.numeric(A1b$loss_C)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_C)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_C<-mean(bootmat[,1])
    ci.loss_C<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_C, lower.loss_C = ci.loss_C[[1]], upper.loss_C= ci.loss_C[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_C<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  
  loss_C<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_C=loss_C)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits1<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits1)
dat_ll1=decayfits1

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                             labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))
```


### Carbon

```{r}
library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_C),
                   sd= sd(loss_C),
                   se=sd(loss_C,na.rm = TRUE)/sqrt(n()))

Carb_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  annotate("text", x = 1, y = 0, label = "ns")+
  annotate("text", x = 2, y = 0, label = "ns")+
  annotate("text", x = 2.75, y = 0, label = "b")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "ab")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = c(0.24,0.80))+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Decomposition constant carbon" ~~( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())


#Carb_decay


ggsave(filename="Figure 2 carbon decay constant.png", plot=Carb_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```




##one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_C )
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```

#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_C)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")
```


```{r}

cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_C)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Carb_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_C , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_C),size=1,linetype=1)+
  scale_y_continuous(limits = c(0,5))+
  labs(colour ="Mesh size")+ 
       xlab( expression(paste("Decomposition constant k "~ ( yrs^ -1 ))))+ylab( expression(paste("Decomposition constant carbon "~( yrs^ -1 ) )))+
  annotate("text", x = 3, y = 4.5, size=4,label = "italic(R^2)==0.777~~~italic(p)<0.001", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Carb_decay

ggsave(filename="Figure 4 Mass decay constant and Carbon decay constant.png", plot=Mass_decay_vs_Carb_decay, device="tiff",height=3.5, width=4, units="in", dpi=600)


```


### Nitrogen

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_N)
A1b$loss_N<- as.numeric(A1b$loss_N)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_N)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_N<-mean(bootmat[,1])
    ci.loss_N<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_N, lower.loss_N = ci.loss_N[[1]], upper.loss_N= ci.loss_N[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_N<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  
  loss_N<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_N=loss_N)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits2<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits2)
dat_ll1=decayfits2

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_N),
                   sd= sd(loss_N),
                   se=sd(loss_N,na.rm = TRUE)/sqrt(n()))

Nitr_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,5))+
  annotate("text", x = 0.75, y = 0, label = "c")+
  annotate("text", x = 1, y = 0, label = "b")+
  annotate("text", x = 1.25, y = 0, label = "a")+
  annotate("text", x = 1.75, y = 0, label = "c")+
  annotate("text", x = 2, y = 0, label = "b")+
  annotate("text", x = 2.25, y = 0, label = "a")+
  annotate("text", x = 2.75, y = 0, label = "b")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "a")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Decomposition constant nitrogen"~~( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

Nitr_decay


ggsave(filename="Figure 2 Nitrogen decay constant.png", plot=Nitr_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```



#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_N )
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```



#### Establish the lmm model

Mass_decay_vs_Nitr_decay

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_N)


##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")


```


```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_N)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```


```{r}
Mass_decay_vs_Nitr_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_N , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_N),size=1,linetype=1)+
  scale_y_continuous(limits = c(0,8))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Nitrogen decomposition constant "~( yrs^ -1 ) )))+
  annotate("text", x = 3, y = 7, size=4,label = "italic(R^2)==0.532~~~italic(p)<0.001", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Nitr_decay

ggsave(filename="Figure 4 Mass decay constant and Nitrogen decay constant.png", plot=Mass_decay_vs_Nitr_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)

```


### Phosphorus

```{r}

A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_P)
A1b$loss_P<- as.numeric(A1b$loss_P)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_P)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_P<-mean(bootmat[,1])
    ci.loss_P<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_P, lower.loss_P = ci.loss_P[[1]], upper.loss_P= ci.loss_P[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_P<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_P<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_P=loss_P)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits3<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits3)
dat_ll1=decayfits3

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_P),
                   sd= sd(loss_P),
                   se=sd(loss_P,na.rm = TRUE)/sqrt(n()))

Phos_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  #annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "ns")+
  #annotate("text", x = 1.25, y = 0, label = "c")+
  annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "a")+
  annotate("text", x = 2.25, y = 0, label = "b")+
  annotate("text", x = 2.75, y = 0, label = "ab")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Phosphorus decomposition constant "~~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Phos_decay


ggsave(filename="Figure 2 Phosphorus decay constant.png", plot=Phos_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```



#### one-way analysis of variance'mesh_size'


```{r}
dat_ll1$transrate=log(dat_ll1$loss_P )
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```



#### Establish the lmm model

Mass_decay_vs_Phos_decay

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_P)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")


```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_P)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Phos_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_P , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_P),size=1,linetype=1)+
  scale_y_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Phosphorus decomposition constant "~( yrs^ -1 ) )))+
  annotate("text", x = 3, y = 3.5, size=4,label = "italic(R^2)==0.577~~~italic(p)<0.001", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Phos_decay


ggsave(filename="Figure 4 mass decay constant and Phosphorus decay constant.png", plot=Mass_decay_vs_Phos_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)
```



### Potassium K

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_K)
A1b$loss_K<- as.numeric(A1b$loss_K)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_K)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_K<-mean(bootmat[,1])
    ci.loss_K<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_K, lower.loss_K = ci.loss_K[[1]], upper.loss_K= ci.loss_K[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_K<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_K<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_K=loss_K)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits4<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits4)
dat_ll1=decayfits4

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_K),
                   sd= sd(loss_K),
                   se=sd(loss_K,na.rm = TRUE)/sqrt(n()))

Pota_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  #annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "ns")+
  #annotate("text", x = 1.25, y = 0, label = "c")+
  annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "a")+
  annotate("text", x = 2.25, y = 0, label = "b")+
  annotate("text", x = 2.75, y = 0, label = "ab")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Potassium decomposition constant"~~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Pota_decay


ggsave(filename="Figure 2 Potassium decay constant.png", plot=Pota_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```



#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_K )
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```


#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_K)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")


```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_K)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Pota_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_K , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_K),size=1,linetype=1)+
  #scale_y_continuous(limits = c(0,4))+
  #scale_x_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Potassium decomposition constant "~( yrs^ -1 ) )))+
  annotate("text", x = 2, y = 3.5, size=4,label = "italic(R^2)==0.476~~~italic(p)<0.001", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
Mass_decay_vs_Pota_decay

ggsave(filename="Figure 4 Mass decay constant and Potassium decay constant.png", plot=Mass_decay_vs_Pota_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)

```



### Calcium

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_Ca)
A1b$loss_Ca<- as.numeric(A1b$loss_Ca)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_Ca)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_Ca<-mean(bootmat[,1])
    ci.loss_Ca<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_Ca, lower.loss_Ca = ci.loss_Ca[[1]], upper.loss_Ca= ci.loss_Ca[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_Ca<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_Ca<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_Ca=loss_Ca)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits5<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits5)
dat_ll1=decayfits5

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_Ca),
                   sd= sd(loss_Ca),
                   se=sd(loss_Ca,na.rm = TRUE)/sqrt(n()))

Calc_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  #annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "ns")+
  #annotate("text", x = 1.25, y = 0, label = "c")+
  #annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "ns")+
  #annotate("text", x = 2.25, y = 0, label = "b")+
  annotate("text", x = 2.75, y = 0, label = "a")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  #theme(legend.position = "none")+
  theme(legend.position = c(0.24,0.80))+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Calcium decomposition constant "~~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Calc_decay


ggsave(filename="Figure 3 Caclium decay constant.png", plot=Calc_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```




#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_Ca )
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```


#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_Ca)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")


```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_Ca)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Calc_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_Ca , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_Ca),size=1,linetype=3)+
  scale_y_continuous(limits = c(0,3))+
  #scale_x_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Calcium decomposition constant "~( yrs^ -1 ) )))+
  #annotate("text", x = 2, y = 3.5, size=4,label = "italic(R^2)==0.476~~~italic(p)<0.001", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Calc_decay

ggsave(filename="Figure 4 Mass decay constant and Calcium decay constant.png", plot=Mass_decay_vs_Calc_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)
```



### Magnesium

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_Mg)
A1b$loss_Mg<- as.numeric(A1b$loss_Mg)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_Mg)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_Mg<-mean(bootmat[,1])
    ci.loss_Mg<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_Mg, lower.loss_Mg = ci.loss_Mg[[1]], upper.loss_Mg= ci.loss_Mg[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_Mg<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_Mg<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_Mg=loss_Mg)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits6<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits6)
dat_ll1=decayfits6

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_Mg),
                   sd= sd(loss_Mg),
                   se=sd(loss_Mg,na.rm = TRUE)/sqrt(n()))

Magn_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  #annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "ns")+
  #annotate("text", x = 1.25, y = 0, label = "c")+
  annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "a")+
  annotate("text", x = 2.25, y = 0, label = "b")+
  annotate("text", x = 2.75, y = 0, label = "a")+
  annotate("text", x = 3, y = 0, label = "a")+
  annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Magnesium decomposition constant "~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Magn_decay


ggsave(filename="Figure 3 Magnesium decay constant.png", plot=Magn_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```




#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_Mg)
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```





#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_Mg)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")



```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_Mg)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```


```{r}
Mass_decay_vs_Magn_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_Mg , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_Mg),size=1,linetype=1)+
  scale_y_continuous(limits = c(0,4))+
  #scale_x_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Magnesium decomposition constant "~( yrs^ -1 ) )))+
  annotate("text", x = 2, y = 3.5, size=4,label = "italic(R^2)==0.384~~~italic(p)<0.01", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Magn_decay

ggsave(filename="Figure 4 Mass decay constant and Magnesium decay constant.png", plot=Mass_decay_vs_Magn_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)
```



### Manganese

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_Mn)
A1b$loss_Mn<- as.numeric(A1b$loss_Mn)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_Mn)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_Mn<-mean(bootmat[,1])
    ci.loss_Mn<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_Mn, lower.loss_Mn = ci.loss_Mn[[1]], upper.loss_Mn= ci.loss_Mn[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_Mn<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_Mn<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_Mn=loss_Mn)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits7<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits7)
dat_ll1=decayfits7

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_Mn),
                   sd= sd(loss_Mn),
                   se=sd(loss_Mn,na.rm = TRUE)/sqrt(n()))

Mang_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,3))+
  #annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "ns")+
  #annotate("text", x = 1.25, y = 0, label = "c")+
  #annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "ns")+
  #annotate("text", x = 2.25, y = 0, label = "b")+
  #annotate("text", x = 2.75, y = 0, label = "a")+
  annotate("text", x = 3, y = 0, label = "ns")+
  #annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Manganese decomposition constant "~~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Mang_decay


ggsave(filename="Figure 3 Manganese decay constant.png", plot=Mang_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)
```




#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_Mn)
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
```



#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_Mn)
hist(dat_ll1$transrate)

##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")



```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_Mn)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Mang_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_Mn , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_Mn),size=1,linetype=3)+
  scale_y_continuous(limits = c(0,3))+
  #scale_x_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Manganese decomposition constant "~( yrs^ -1 ) )))+
  #annotate("text", x = 2, y = 3.5, size=4,label = "italic(R^2)==0.384~~~italic(p)<0.01", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Mang_decay

ggsave(filename="Figure 4 Mass decay constant and Manganese decay constant.png", plot=Mass_decay_vs_Mang_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)

```




### Condensed tannins

```{r}
A1b<- d1ll %>% dplyr::select(species,tree_quality,Nitrogen_added,mesh_size,number, Time_at_harvest,k,C_initial,N_initial,P_initial,
                             K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial,loss_Tannin)
A1b$loss_Tannin<- as.numeric(A1b$loss_Tannin)
library(tidyr)
dt<-A1b %>% drop_na()
#View(dt)
str(dt)
dt$mass_remaining<- (100- dt$loss_Tannin)/100
data_aggregated <- dt %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size, number,Time_at_harvest,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>% # Group by the identifier and time columns
  dplyr::summarize(value = mean(mass_remaining, na.rm = TRUE)) %>% # Aggregate (take the mean)
  ungroup()
any(is.na(data_aggregated $value))

# Reshape the data for litterfitter
lit <-data_aggregated 

lit$mass_remaining=lit$value
lit$Time_at_harvest<- as.character(as.character(lit$Time_at_harvest))  
lit$Time_at_harvest<- as.numeric(as.character(lit$Time_at_harvest))
lit$time_yrs<- lit$Time_at_harvest/365

#View(lit)
library("dplyr")

x2 <- lit[which(lit$mass_remaining < 1),]
#View(x2)

library(litterfitter)
library(dplyr)
library(tibble)
library(litterfitter)
library(dplyr)
library(tibble)


options(na.action = "na.omit")

# turn a list of dataframes into a long dataframe
list_to_df <- function(mylist){
  
  # make a vector of row ids that correspond to the list names
  rowid.indx <- lapply(mylist, function(x) dim(x)[1])
  sourceVec.list <- list()
  for(i in 1:length(rowid.indx)){
    sourceName <- names(rowid.indx)[i]
    numRows <- rowid.indx[[i]]
    sourceVec.list[[i]] <- rep(sourceName, numRows)
  }
  rowVec <- unlist(sourceVec.list)
  
  # combine into df
  df <- data.frame(do.call(rbind, mylist))
  df$source <- rowVec
  
  return(df)
}


# calculate decay trajectory fits for each species per treatment 
Calc_R2<-function(w.fits){
  
  pred<-w.fits[['predicted']]
  mass<-w.fits[['mass']]
  
  sstot<-sum((mass - mean(mass))^2)
  ssres<-sum((pred - mass)^2)
  r2<-1-(ssres/sstot)
  
  return(r2)
}



# decay fits
fit_all_curves<-function(df_in, lit){
  
  #df_in <- pmr  #testing stuff
  
  #negative expon fit
  ne_fits <- lapply(split(df_in, factor(df_in$species)),function(x){
    fit_litter(time = x$time_yrs, 
               mass.remaining = x$mass_remaining, model = c("neg.exp"), iters = 1000)
  })
  #create bootstrap distrib and get the 95% CI
  boot.ne<-lapply(ne_fits, function(x){
    bootmat<-bootstrap_parameters(x, nboot=10) 
    #plot(bootmat)
    mean.loss_Tannin<-mean(bootmat[,1])
    ci.loss_Tannin<-quantile(bootmat[,1], c(.05, .95))
    result<-data.frame(mean.loss_Tannin, lower.loss_Tannin = ci.loss_Tannin[[1]], upper.loss_Tannin= ci.loss_Tannin[[2]])
    return(result)
  })
  boot.ne.df <- list_to_df(boot.ne)
  # from ne model
  loss_Tannin<-unlist(lapply(ne_fits, function(x) x$oPpimFit$par))
  t50<-unlist(lapply(ne_fits, function(x) time_to_prop_mass_remaining(x,threshold.mass=0.5)))
  neg.exp.aic<-unlist(lapply(ne_fits, function(x) x$fitAICc))
  ne.r2<-unlist(lapply(ne_fits, function(x) Calc_R2(x)))
  loss_Tannin<-unlist(lapply(ne_fits, function(x) x$optimFit$par))
  # put everything in a dataframe
  spdf<-data.frame(loss_Tannin=loss_Tannin)
  spdf$species<-rownames(spdf)
  
  return(spdf)
}  
neg.exp<-litterfitter:::neg.exp


decayfits8<-x2 %>%
  group_by(species,tree_quality,Nitrogen_added,mesh_size,number,k,C_initial,N_initial,P_initial,
           K_initial,Ca_initial,Mg_initial,Mn_initial,Tannin_initial) %>%
  do(data.frame(fit_all_curves(.)))
#View(decayfits8)
dat_ll1=decayfits8

dat_ll1$Nitrogen_added <- factor(dat_ll1$Nitrogen_added,levels = c("N_0", "N_2", "N_6"), 
                                 labels = c(expression(N[0]), expression(N[2]), expression(N[6])))

dat_ll1$mesh_size <- factor(dat_ll1$mesh_size,levels = c("0.07 mm", "2 mm", "5 mm"))


library(dplyr)
library(ggplot2)
dat_ml1<-dat_ll1 %>% group_by(Nitrogen_added, mesh_size)%>%
  dplyr::summarise(ml= mean(loss_Tannin),
                   sd= sd(loss_Tannin),
                   se=sd(loss_Tannin,na.rm = TRUE)/sqrt(n()))

Cond_decay=ggplot(dat_ml1,aes(mesh_size,ml,color=Nitrogen_added))+
  geom_rect(data=NULL,aes(xmin=1.5,xmax=2.5,ymin=-Inf,ymax=Inf),
            fill="#E8E8E8", colour = NA, alpha = 0.1)+
  geom_point(position = position_dodge(0.9),stat="identity",size=3)+
  geom_errorbar(ymax=dat_ml1$ml+dat_ml1$se,ymin=dat_ml1$ml-dat_ml1$se, width=0.3, position = position_dodge(0.9))+
  scale_y_continuous(limits = c(0,6))+
  annotate("text", x = 0.75, y = 0, label = "a")+
  annotate("text", x = 1, y = 0, label = "a")+
  annotate("text", x = 1.25, y = 0, label = "b")+
  #annotate("text", x = 1.75, y = 0, label = "ab")+
  annotate("text", x = 2, y = 0, label = "ns")+
  #annotate("text", x = 2.25, y = 0, label = "b")+
  #annotate("text", x = 2.75, y = 0, label = "a")+
  annotate("text", x = 3, y = 0, label = "ns")+
  #annotate("text", x = 3.25, y =0, label = "b")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F"),
                     labels = c(expression(N[0]), expression(N[2]), expression(N[6])))+
  theme(legend.position = "none")+
  labs( colour="N addition")+
  xlab("Mesh size")+
  ylab(expression(paste( "Tannins decomposition constant"~~ ( yrs^ -1 ))))+guides(color=guide_legend(order=2),shape=guide_legend(order=1))+
  theme(plot.title =element_text(hjust = 0.5,size=(11)))+
  theme(
    legend.direction = "vertical",
    legend.text = element_text(size=11))+
  theme(legend.title=element_text(size=(11)))+
  theme(axis.title = element_text(family = "palatino", size = (11), colour = "black"))+
  theme(axis.text = element_text(family = "palatino", colour = "black", size = (12)))+ 
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank())

#Cond_decay


ggsave(filename="Figure Conddensed tannins decay constant.png", plot=Cond_decay, device="tiff",
       height=3.5, width=4, units="in", dpi=600)
```


#### one-way analysis of variance'mesh_size'

```{r}
dat_ll1$transrate=log(dat_ll1$loss_Tannin)
dat_ll1_fine=dat_ll1[dat_ll1$mesh_size=="0.07 mm",]
dat_ll1_med=dat_ll1[dat_ll1$mesh_size=="2 mm",]
dat_ll1_big=dat_ll1[dat_ll1$mesh_size=="5 mm",]
result <- aov(dat_ll1_fine$transrate ~ dat_ll1_fine$Nitrogen_added, data = dat_ll1_fine)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_med$transrate ~ dat_ll1_med$Nitrogen_added, data = dat_ll1_med)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)
result <- aov(dat_ll1_big$transrate ~ dat_ll1_big$Nitrogen_added, data = dat_ll1_big)
summary(result)
tukey_result <- TukeyHSD(result)
print(tukey_result)

```



#### Establish the lmm model

```{r}
##Inverse normal transformation（Inverse Normal Transformation）
hist(dat_ll1$loss_Tannin)


##Run package
library(lme4)
library(lmerTest)
library(pbkrtest)
##Build full model Consider interaction
mod4=lmer(data=dat_ll1, transrate~Nitrogen_added*mesh_size+(1|species))
summary(mod4)
anova(mod4)

###似然比检验模型
model_no_3way <- update(mod4, . ~ . - mesh_size:Nitrogen_added)
anova(model_no_3way)
anova(mod4,model_no_3way)

###r2检验
library(MuMIn)
r2 <- r.squaredGLMM(mod4)
r2
##Diagnostic model
plot(mod4)
qqnorm(resid(mod4), main = "Q-Q图（残差）")



```

```{r}
cor_test <- cor.test(dat_ll1$k, dat_ll1$loss_Tannin)
cor_value <- round(cor_test$estimate, 3)
cor_value
p_value <- round(cor_test$p.value, 4)
cor_test$p.value
```

```{r}
Mass_decay_vs_Cond_decay=ggplot()+ geom_point(data = dat_ll1, 
                        aes(y = loss_Tannin , x =k),
                        alpha = 0.5, 
                        size = 3) + 
  geom_smooth(data=dat_ll1,method = "lm",colour= "black" ,se=TRUE, aes(x=k , y= loss_Tannin),size=1,linetype=3)+
  scale_y_continuous(limits = c(0,6))+
  #scale_x_continuous(limits = c(0,4))+
  labs(colour ="Mesh size")+ 
  xlab( expression(paste("Decomposition constant k " ~( yrs^ -1 ))))+ylab( expression(paste("Tannins decomposition constant "~( yrs^ -1 ) )))+
  #annotate("text", x = 2, y = 3.5, size=4,label = "italic(R^2)==0.384~~~italic(p)<0.01", parse=TRUE, colour= "black" ) +
  theme(legend.position = c(0.2,0.85))+
  theme(plot.title =element_text(hjust = 0.5,size=(12)))+
  theme(axis.line = element_line(colour = "black", size = 0.5),
        axis.ticks.x=element_line(colour = "black"),
        axis.ticks.y=element_line(colour = "black"),
        axis.ticks.length = unit(-0.15, "cm"),
        axis.text = element_text(colour = "black", size = 10),
        axis.title = element_text(colour = "black", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill=NA,color="black", size=0.5, linetype="solid"),
        panel.background = element_blank(),
        strip.text = element_text(colour = "black", size = 12),
        legend.text=element_text(size=10,face="bold.italic"),
        legend.background = element_blank(),
        legend.key.width=unit(0.2,"cm"),
        legend.key.height=unit(0.2,"cm"))+
  guides(fill="none")+
  scale_color_manual(values =c("#576904","#A98645","#ADFF2F","#A45378","#EFC000"))
#Mass_decay_vs_Cond_decay


ggsave(filename="Figure 4 Mass decay constant and Condensed tannins decay constant.png", plot=Mass_decay_vs_Cond_decay, device="tiff",
       height=4, width=4, units="in", dpi=600)


```


Create fig2.fig3,fig4,table3

```{r}
Fig2<-(Carb_decay+Nitr_decay)/(Phos_decay+Pota_decay)
ggsave(filename="Figure 2.png", plot=Fig2, device="tiff",
       height=3, width=9, units="in", dpi=600)
Fig2

```

Figure 2

```{r}
Fig3<-(Calc_decay+Magn_decay)/(Mang_decay+Cond_decay)
ggsave(filename="Figure 3.png", plot=Fig3, device="tiff",
       height=3, width=9, units="in", dpi=600)
Fig3

```

Figure 3


```{r}
Fig4<-(Mass_decay_vs_Carb_decay+Mass_decay_vs_Nitr_decay)/(Mass_decay_vs_Phos_decay+Mass_decay_vs_Pota_decay)/Mass_decay_vs_Magn_decay
ggsave(filename="Figure 4.png", plot=Fig2, device="tiff",
       height=3, width=9, units="in", dpi=600)
Fig4

```

Figure 4

# Conclusions

Nitrogen addition level, litter quality, mesh size and their interactions significantly influenced the litter decomposition rates. As for litter decomposition rate, macrofauna showed higher sensitivity to nitrogen addition, while mesofauna and microorganisms exhibited lower sensitivity, particularly under high nitrogen addition treatments. Nitrogen addition significantly influenced the release rates of carbon, nitrogen, phosphorus, potassium, calcium, magnesium, and condensed tannin, litterbags mesh size significantly affected the release rates of carbon, nitrogen, phosphorus, potassium, calcium, and magnesium. Nitrogen addition promotes the release of nitrogen from litter, while high levels of nitrogen addition inhibit the release of elements such as, calcium and magnesium, particularly pronounced in the presence of macrofauna. This indicates that when predicting the impacts of global environmental changes such as N deposition on ecosystem processes (e.g., nutrient cycling), the functional trait distribution (e.g., body size) within the biological community must be explicitly considered. Scientific evidence can be provided to support sustainable forest management.







